All stable state plots, with only the maximum tolerance strain

### 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e4 wait_time/allssplots_strainvar_0.9.1.Rmd

---
title: All stable state plots, with strain variation, 6 strains
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))

>>>>

---
title: All stable state plots, with strain variation, 1e4 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

### 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e6 wait_time/allssplots_maxtol_0.9.1.Rmd

---
title: All stable state plots, with strain variation, 1e4 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

>>>>

---
title: All stable state plots, with only the maximum tolerance strain
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_-1strains_waittime", wait_time, "_event_definition_2.RDS")))
